Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-29 paper/paper.tex

Tappi 2017 \cite{Tappi2017ComputerVS},
The evaluation of fish freshness can be per- formed using chemical, sensory and physical methods. Besides sensory methods, several instrumental techniques have been applied with the objective of replacing sensory assessment. The aim of this study was to set up and test objective physical methods mainly based on computer vision system (CVS) to assess red mullet (Mullus barba- tus) freshness evolution during 10 days of storage, at two different storage temperatures (0 and 4 °C). To check the effectiveness of the purposed physical methods, CVS fea- tures (loss in the epidermis pigmentation, development of gill mucus and eye concavity index) and firmness have been compared with chemical trimethylamine content and sensory (QIM) attribute scores. As expected, fish degrada- tion was faster at the higher temperature. Instrumental tex- ture evaluation of fish by penetration test enabled to detect distinctive firmness changes due to onset and resolution of rigor mortis, and the successive tenderization phenomenon. Among CVS parameters, the epidermis pigmentation loss, and particularly the eye shape modification (eye concavity index) evidenced a high sensibility for the estimation of fresh red mullet quality loss, as a function of the two differ- ent storage conditions, and a good agreement with trimeth- ylamine content and QIM response evolution.

>>>>

3D Segmentation from microCT\newline
Bock 2018 \cite{BockAlexander2018TITE},

Computer Vision Overviews Related to Fish\newline
G{\"u}m{\"u}\c{s} 2011 \cite{Gm2011MachineVA},

Tappi 2017 \cite{Tappi2017ComputerVS},
The evaluation of fish freshness can be per- formed using chemical, sensory and physical methods. Besides sensory methods, several instrumental techniques have been applied with the objective of replacing sensory assessment. The aim of this study was to set up and test objective physical methods mainly based on computer vision system (CVS) to assess red mullet (Mullus barba- tus) freshness evolution during 10 days of storage, at two different storage temperatures (0 and 4 °C). To check the effectiveness of the purposed physical methods, CVS fea- tures (loss in the epidermis pigmentation, development of gill mucus and eye concavity index) and firmness have been compared with chemical trimethylamine content and sensory (QIM) attribute scores. As expected, fish degrada- tion was faster at the higher temperature. Instrumental tex- ture evaluation of fish by penetration test enabled to detect distinctive firmness changes due to onset and resolution of rigor mortis, and the successive tenderization phenomenon. Among CVS parameters, the epidermis pigmentation loss, and particularly the eye shape modification (eye concavity index) evidenced a high sensibility for the estimation of fresh red mullet quality loss, as a function of the two differ- ent storage conditions, and a good agreement with trimeth- ylamine content and QIM response evolution.
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU},
Saitoh 2015 \cite{Saitoh2015ImagebasedFR},
Sung 2017 \cite{Sung2017VisionBR},
Sharmin 2019 \cite{Sharmin2019MVB},
Salman 2016 \cite{Salman2016FishSC},
Sung 2020 \cite{Sung2020AutomaticGF},
Xu 2021 \cite{Xu2021TransferLA},
Banan 2020 \cite{Banan2020DeepLA}
Ogunlana 2015 \cite{Ogunlana2015FCU},
Sayed 2018 \cite{SayedGehadIsmail2018AAFS},
Rodrigues 2015 \cite{RodriguesMarcoT.A2015Ecda},
Shah 2019 \cite{Shah2019FishPakFS},
